---
title: "first_RMD"
author: "lisanechyporenko"
date: "2021-02-19"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

```{r}
data("mtcars")

plot(mtcars$drat, mtcars$mpg)
```

##Exercises

Tasks:

1. Create tables for Diagnosis.Age, Sex, Race.Category and American.Joint.Committee.on.Cancer.Tumor.Stage.Code

Solution:
```{r ex 1}
library(tidyverse)

luad_data <- read.delim("D:/Master/R_Kurs/Workflow/data/luad_tcga_pan_can_atlas_2018_clinical_data.tsv", header=TRUE)

tab_1 <- luad_data %>% select(c("Diagnosis.Age","Sex","Race.Category","American.Joint.Committee.on.Cancer.Tumor.Stage.Code")) %>% table()

```

2. do chi-sq test for American.Joint.Committee.on.Cancer.Tumor.Stage.Code and Sex Plot the data (e.g. barplot, counts by gender)

```{r ex 2}

luad_data %>% filter(!is.na(Sex)) %>%  
   ggplot(aes(Sex,fill=American.Joint.Committee.on.Cancer.Tumor.Stage.Code)) + geom_bar(position="dodge")

tab_1 <- luad_data %>% select(c("Sex","American.Joint.Committee.on.Cancer.Tumor.Stage.Code")) %>% table()

Chi_test <- chisq.test(tab_1)
```

3. do linear regression for the Mutation.Count and stage, gender and age. show the results in table. Plot the data.

```{r ex 3}

library(openintro)
library(broom)

```

First compare Mutation count data with age:


```{r}

luad_age <- luad_data %>% select(c("Mutation.Count","Diagnosis.Age"))  %>% ggplot(aes(Diagnosis.Age,Mutation.Count)) 

luad_age + geom_point() + geom_smooth(method = "lm", se = FALSE)

m1 <- lm(Mutation.Count ~ Diagnosis.Age, data = luad_data)

```

Second compare Mutation count data with the stage:

```{r}

luad_stage <- luad_data %>% select(c("Mutation.Count","American.Joint.Committee.on.Cancer.Tumor.Stage.Code"))  %>% ggplot(aes(American.Joint.Committee.on.Cancer.Tumor.Stage.Code, Mutation.Count)) 

luad_stage + geom_boxplot()

m2 <- lm(Mutation.Count ~ American.Joint.Committee.on.Cancer.Tumor.Stage.Code, data = luad_data)

```

Third compare Mutation count data with the gender:

```{r}

luad_age <- luad_data %>% select(c("Mutation.Count","Sex"))  %>% filter(!is.na(Sex)) %>%  ggplot(aes(Sex, Mutation.Count), color = Sex) 

luad_age + geom_boxplot()

m3 <- lm(Mutation.Count ~ Sex, data = luad_data)

```
